Future challenges for Research Software Engineering

### 2025-05-19 future_challenges_for_RSEng.tex
one more notion
Update future_challenges_for_RSEng.tex
Co-authored-by: Gerasimos Chourdakis <gerasimos.chourdakis@ipvs.uni-stuttgart.de>

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious.
Kim is currently designing the software service stack at the university.
She increasingly struggles to find compelling Open Source alternatives that enables them to keep complete control of their data
rather than relying on software and tools that are backed by large, foreign corporate entities.
So far, she still has the support of the university board, since it values strategic autonomy.
Kay used to work on a project that developed
software for cheap water monitoring devices in the Global South, but now funding has dried up.
Having gone through another fixed term contract he is now fed up
with work in academia and decides that its time limited contracts are not attractive.
Now Governments around the world are struggling to reposition themselves in this emerging de-globalised world with its new blocks and therefore have de-prioritised publicly funded research.
Kay sees the writings on the wall and decides to work for a defence company since they offer more secure employment in this polarised world.
\end{story}

>>>>

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious.
Kim is currently designing the software service stack at the university.
She increasingly struggles to find compelling Open Source alternatives that enables them to keep complete control of their data
rather than relying on software and tools that are backed by large, foreign corporate entities.
So far, she still has the support of the university board, since it values strategic autonomy.
Kay used to work on a project that developed
software for cheap water monitoring devices in the Global South, but now funding has dried up.
Having gone through another fixed term contract, he is now fed up
with work in academia and decides that its time limited contracts are not attractive.
Now Governments around the world are struggling to reposition themselves in this emerging de-globalised world with its new blocks and therefore have de-prioritised publicly funded research.
Kay sees the writings on the wall and decides to work for a defence company since they offer more secure employment in this polarised world.
\end{story}
